---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# acroname

<!-- badges: start -->
<!-- badges: end -->

## Installation


```{r, eval = FALSE}
devtools::install_github("vpnagraj/acroname")
```

## Features

- `acronym()`: Generate acronym from input string
- `initialism()`: Generate initialism from input string
- `mince()`: Prepare input string

## Usage

### Basic example 

The minimal usage for creating an acronym:

```{r}
library(acroname)
set.seed(123)
acronym("super special software package", acronym_length = 5)
```

And an initialism for the same string:

```{r}
initialism("super special software package")
```

The functions can accept input character vectors that either contain the string in a single element or are prepared with one element per word:

```{r}
acronym(c("super", "special", "software", "package"), acronym_length = 5)
```

### Convert result to `tibble`

Both `acronym()` and `initialism()` include an option to return the result as a `tibble` object:

```{r}
acronym("dip him in the river who loves water", acronym_length = 4, to_tibble = TRUE)
```

### Exclude articles

Each function can also be customized to exclude articles in the input string:

```{r}
initialism("dip him in the river who loves water", to_tibble = TRUE, ignore_articles = TRUE)
```

### Trigger "bag of words" approach

Using the "bow" option will trigger processing using a "bag of words" method, by which words in the input string are randomly selected. The number of words selected from the input string depends on the value passed to the "bow_prop" argument:

```{r}
acronym("dip him in the river who loves water the fountain contains the cistern overflows", ignore_articles = TRUE, acronym_length = 4, bow = TRUE, bow_prop = 0.75)
```

It is possible to generate a series of randomized results by iterating over the function:

```{r}
library(purrr)
library(dplyr)

## write a function to wrap acronym() in order to map
mapwrap <- function(i, input) {
  res <- 
    acronym(input = input, ignore_articles = TRUE, acronym_length =  4, bow = TRUE, bow_prop = 0.75, to_tibble = TRUE) %>%
    mutate(iteration = i, .before = "formatted")
  return(res)
}

iterations <- paste0("iteration_",1:5)
map_df(iterations, mapwrap, "dip him in the river who loves water the fountain contains the cistern overflows")
```

### Use a custom dictionary

By default the `acronym()` engine will search for acronyms that match words in the "en_US" dictionary provided by the [hunspell](https://CRAN.R-project.org/package=hunspell) package. However, the dictionary of words to match can be customized via the "dictionary" argument. The example below uses a dictionary based on names from the dplyr package, prepared with a little help from the `mince()` function:

```{r}
## get names (first or last) from the dplyr::starwars data
## see mince() in action
mince(starwars$name)

sw_names <- mince(starwars$name)$words

acronym("latest and greatest data analysis package", dictionary = sw_names, acronym_length = 4)
```


### Configure timeout option

Depending on the characters in the input string, the size of dictionary, and the acronym length it may not be possible to generate an acronym that matches a word in the dictionary. The `acronym()` function will try for 60 seconds by default, but this duration can be customized via the "timeout" argument:

```{r, error=TRUE, message=TRUE}
## the longer the desired acronym, the longer it will likely to take to find a match
## setting the timeout to 2 seconds here
acronym("latest and greatest data analysis package", dictionary = sw_names, acronym_length = 10, timeout = 2)

```


## Related

- https://github.com/bacook17/acronym
